### 2019-09-15 scache/tii/tex/model.tex
Resubmittion version

In this section, we introduce \textit{Framework Resources Quantification} (FRQ) model to evaluate the performance of DAG frameworks.
% The FRQ model quantifies computing and I/O resources and visualizes them in the time dimension.
The FRQ model is able to predict the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, etc.
% The FRQ model assist us in analyzing the resource scheduling of DAG framework and evaluate their performance.
We first introduce the FRQ model in Subsection \ref{model_overview}. In Subsection \ref{model_analysis}, we use the FRQ model to describe different computation jobs and discuss their performance.
% In the last Subsection \ref{model_evaluation}, we use the actual experimental results to evaluate the FRQ model.

\subsection{The FRQ Model}\label{model_overview}
% The current distributed computing frameworks mostly use DAGs to describe the computation logic. 
% A shuffle phase is required between each adjacent DAG computation phases.
{\color{black}
We propose the FRQ model to better analyze the relationship between the computation phase and the shuffle phase in the DAG computing.
% The FRQ model focuses on describing the overhead caused by the shuffle process.
The FRQ model focuses on describing the shuffle overhead which significantly effected by the scheduling strategy.
% This overhead does not only depends on the input data size, computation speed, complexity of algorithms, and other parameters but also on which scheduling strategy the job takes.
% By using the FRQ model, we can analyze the advantages of each strategy in various situations.
After quantifying computing and I/O resources, we use the FRQ model to evaluate different resource scheduling strategies.
% For convenience, we introduce the FRQ model by taking a simple MapReduce job as an example in this section.

@@

The formulas of map phase time and shuffle phase time are as follow:
% \(T_{Map}={{\frac{D}{V_{Map}}}}\).
\begin{equation}
\label{equation_Tmap}
\begin{aligned}
    T_{Map} &= {{\frac{D}{V_{Map}}}}
\end{aligned}
\begin{aligned}
    T_{Shuffle} &= {{\frac{D}{V_{Shuffle}}}}
\end{aligned}
\end{equation}

>>>>

In this section, we introduce \textit{Framework Resources Quantification} (FRQ) model to evaluate the performance of DAG frameworks.
% The FRQ model quantifies computing and I/O resources and visualizes them in the time dimension.
The FRQ model is able to predict the execution time required by the application under most circumstances, including different DAG frameworks, hardware environments, etc.
% The FRQ model assist us in analyzing the resource scheduling of DAG framework and evaluate their performance.
We first introduce the FRQ model in Subsection \ref{model_overview}. In Subsection \ref{model_analysis}, we use the FRQ model to describe different computation jobs and discuss their performance.
% In the last Subsection \ref{model_evaluation}, we use the actual experimental results to evaluate the FRQ model.

\subsection{The FRQ Model}\label{model_overview}
% The current distributed computing frameworks mostly use DAGs to describe the computation logic. 
% A shuffle phase is required between each adjacent DAG computation phases.
{\color{black}
We propose the FRQ model to better analyze the relationship between the computation phase and the shuffle phase in the DAG computing.
% The FRQ model focuses on describing the overhead caused by the shuffle process.
The FRQ model focuses on describing the shuffle overhead which is significantly affected by the scheduling strategy.
% This overhead does not only depends on the input data size, computation speed, complexity of algorithms, and other parameters but also on which scheduling strategy the job takes.
% By using the FRQ model, we can analyze the advantages of each strategy in various situations.
After quantifying computing and I/O resources, we use the FRQ model to evaluate different resource scheduling strategies.
% For convenience, we introduce the FRQ model by taking a simple MapReduce job as an example in this section.

@@

The formulas of map phase time and shuffle phase time are as follows:
% \(T_{Map}={{\frac{D}{V_{Map}}}}\).
\begin{equation}
\label{equation_Tmap}
\begin{aligned}
    T_{Map} &= {{\frac{D}{V_{Map}}}}
\end{aligned}
\begin{aligned}
    T_{Shuffle} &= {{\frac{D}{V_{Shuffle}}}}
\end{aligned}
\end{equation}

### 2019-09-15 scache/tii/tex/optimization.tex
Resubmittion version

In distributed computing, we use shuffle to do all-to-all data transfer among the nodes.
For a clear illustration, we divide a computing job into three phases: map, shuffle, and reduce.
In most of the DAG frameworks, including Spark, Hadoop MapReduce, and Tez, shuffle phase is couple with reduce phase which means that shuffle data transfer and reduce computing start simultaneously.
On the reduce side, shuffle introduces an explicit overhead during shuffle read.
% Because the reduce computing depends on the shuffle results, the waiting for the shuffle data causes the overhead.
% because all reduce tasks start shuffle read simultaneously, 
Furthermore, the synchronized shuffle read causes a burst of network traffic and further enlarge the overhead.

% To better illustrate the shuffle optimization, we use this formula to represent the job completion time: \(T_{Job}=T_{Map}+T_{Reduce}+T_{overhead}\). \(T_{Map}\) represents the completion time of map phase and \(T_{Reduce}\) represents the reduce phase time without being affected by the coupled shuffle phase. 
% We use \(T_{overhead}\) to represent the above-mentioned overhead caused by shuffle.
% In the following subsections, we introduce how we decouple the shuffle and use pre-fetching and memory cache to mitigate the overhead.
To mitigate the shuffle overhead, we propose an optimization to overlap the shuffle data transfer in multi-round map tasks, and uses memory to cache the shuffle data. To achieve this optimization:
\begin{itemize}
	\item Shuffle phase should be decoupled from reduce phase to achieve a better scheduling scheme.
	\item Reduce tasks should be pre-scheduled in map phase to achieve shuffle data pre-fetching.
\end{itemize}
% In Section \ref{model}, we also propose a performance model called the FRQ to model the optimization.
}

@@

SCache cache the shuffle data on the memory instead of storing on disk liked Spark or Hadoop MapReduce.
In this aspect, SCache optimizes the time of shuffle read and shuffle write since memory gets better I/O performance.
}
% To achieve the decoupling of map tasks and reduce tasks, the original shuffle write and read implementation in the current frameworks should be modified to apply the API of SCache.
% To prevent the release of a slot being blocked by shuffle write,  
% SCache provides a disk-write-like API named $putBlock$ to handle the storage of partitioned shuffle data blocks produced by a map task.
% Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks to SCache's reserved memory and release the slot immediately.
% Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks out of map tasks and store them in the reserved memory.
% After the memory copy, the slot will be released immediately.

@@

To optimize shuffle phase, we propose a co-scheduling scheme with two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}). 
The DAG frameworks follow the co-scheduler to starts reduce tasks.
}
% The pre-scheduling and pre-fetching are the most critical aspects of the optimization. 
% The task-node mapping is not determined until tasks are scheduled by the scheduler of DAG framework. 
% Once the tasks are scheduled, the slots will be occupied to launch them. 
% And the shuffle data cannot be pre-fetched without the awareness of task-node mapping.
% We propose a co-scheduling scheme with two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}). 
% That is, the task-node mapping is established a priori, and then it is enforced by the co-scheduler when the DAG framework starts task scheduling.

@@

To illustrate the case, we present a particular spark job which using the Spark RangePartitioner in Figure \ref{fig:range_pre_sample}. 

@@

Due to the extremely high data skew introducing by the partition, the linear regression model cannot fit the result well.

@@

}
During both of the predictions, the composition of each reduce partition is calculated as well. We define $prob_i$ as
\begin{equation}
\label{equationprob}
\begin{aligned}
	prob_i &= \max_{0 \leq j \leq m} \frac{BlockSize_{kji}}{reduceSize_i} \\
	m &= \text{number of map tasks}
\end{aligned}
\end{equation}
% Note that a balanced schedule decision can be made under the consideration of the size of each reduce task, and the size of a reduce task produced by one shuffle $reduceSize_i = \sum_{j=0}^{m} {BlockSize_{ji}}$, 
% where the $m$ is the number of map tasks that can be easily extracted from DAG information;
The $reduceSize_i$ represents the size of a reduce task, which is represented by $reduceSize_i = \sum_{j=0}^{m} {BlockSize_{ji}}$.
We use $prob_i$ to achieve a better data locality while performing shuffle pre-scheduling. 
% This parameter is used to achieve a better data locality while performing shuffle pre-scheduling.

\subsubsection{Heuristic MinHeap Scheduling}\label{h-minheap}
% As long as the input sizes of reduce tasks are available, the pre-scheduling is a classic scheduling problem without considering the data locality. 
% But ignoring the data locality can introduce extra network transfer. 
% In order to balance load while minimizing the network traffic, we present the Heuristic MinHeap Scheduling algorithm (Algorithm \ref{hminheap}).
To balance load while minimizing the network traffic, we present the \textit{Heuristic MinHeap Scheduling} algorithm (Algorithm \ref{hminheap}).
{\color{black}
% For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum. 
To keep the pre-scheduling load balance, we maintain a min-heap in the first $while$ loop (i.e., line 6-11).
We use the min-heap to simulate the load of each node and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum.
Spark FIFO only can achieve $2\text{-}approximation$ optimum.
}
% Since the sizes of tasks are considered while scheduling, \textit{Heuristic MinHeap Scheduling} can achieve a shorter makespan than Spark FIFO which is a $2\text{-}approximation$ optimum. 
% Simulation of OpenCloud trace in Figure \ref{fig:sim} also shows that \textit{Heuristic MinHeap Scheduling} has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
After pre-scheduling, the task-node mapping will be adjusted according to the locality. 
The $SWAP\_TASKS$ will be triggered when the $host\_id$ of a task does not equal the $assigned\_id$.
Based on the $prob$, the normalized probability $norm$ is calculated as a bound of performance degradation. 
Inside the $SWAP\_TASKS$, tasks will be selected and swapped without exceeding the $upper\_bound$.
Since the algorithm only maintains a min-heap and traverses $reduce$ for swapping, the algorithm needs $O(n)$ operations.

@@

\begin{minipage}{0.95\columnwidth}
\begin{algorithm}[H]
\caption{Heuristic MinHeap Scheduling for Single Shuffle}
\label{hminheap}
	\begin{algorithmic}[1]
	\small
	\Procedure{schedule}{$m, host\_ids, p\_reduces$}
		\State $m\gets$ partition number of map tasks
		\State $R\gets$ sort $p\_reduces$ by size in non-increasing order
		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
		\State $idx\gets 0$
		\While{$idx <$ len$R$}
		% \Comment{Schedule reduces by MinHeap}
		\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
		\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
		\State $R\left[idx\right].assigned\_id \gets M \left[0\right].host\_id$
		\State Sift down $M\left[0\right]$ by $size$
		\State $idx\gets idx+1$
		\EndWhile
		\State $max\gets$ maximum size in $M$
		% \State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
		\ForAll{$reduce$ in $R$}
		\Comment{Heuristic locality swap}
			\If{$reduce.assigned\_id \neq reduce.host\_id$}
				\State $p\gets reduce.prob$
				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
				\State $upper\_bound \gets \left(1 + norm\right) \times max$
				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
			\EndIf
		\EndFor
		\Return $M$
	\EndProcedure
	\Procedure{swap\_tasks}{$M, reduce, upper\_bound$}
		\State Swap tasks between node $host\_id$ and node $assigned\_id$
		\State of $reduce$ without exceeding the $upper\_bound$
		\State of both nodes.
		\State Return if it is impossible.
	\EndProcedure
	\end{algorithmic}
\end{algorithm}
\end{minipage}

@@

\subsubsection{Cope with Multiple Shuffle Dependencies}
{\color{black}
A reduce stage can have more than one shuffle dependency in the current DAG computing frameworks.
To cope with multiple shuffle dependencies, we present the \textit{Accumulated Heuristic Scheduling} algorithm.
}
% The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
% For those pending shuffles, it is impossible to predict their sizes. 
% This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
% But doing this introduces large overhead such as extra task serialization. 
% To avoid violating the optimization from framework, we present the \textit{Accumulated Heuristic Scheduling} algorithm to cope with multiple shuffle dependencies.
As illustrated in Algorithm \ref{mhminheap}, the sizes of previous \textit{shuffles} scheduled by \textit{Heuristic MinHeap Scheduling} are counted. 
When a new shuffle starts, the predicted $size$, $prob$, and $host\_id$ in $p\_reduces$ are accumulated with previous \textit{shuffles}. 
After scheduling, if the newly $assigned\_id$ of a reduce task did not equal the original one, a re-shuffle will be triggered to transfer data to the new host. 
This re-shuffle is rare since the previous shuffle data contributes a huge composition (i.e., high $prob$) after the accumulation, 
which leads to a higher probability of tasks swap in $SWAP\_TASKS$.

>>>>

In distributed computing, we use shuffle to do all-to-all data transfer among the nodes.
For a clear illustration, we divide a computing job into three phases: map, shuffle, and reduce.
In most of the DAG frameworks, including Spark, Hadoop MapReduce, and Tez, shuffle phase is coupled with reduce phase which means that shuffle data transfer and reduce computing start simultaneously.
On the reduce side, shuffle introduces an explicit overhead during shuffle read.
% Because the reduce computing depends on the shuffle results, the waiting for the shuffle data causes the overhead.
% because all reduce tasks start shuffle read simultaneously, 
Furthermore, the synchronized shuffle read causes a burst of network traffic and further enlarges the overhead.

% To better illustrate the shuffle optimization, we use this formula to represent the job completion time: \(T_{Job}=T_{Map}+T_{Reduce}+T_{overhead}\). \(T_{Map}\) represents the completion time of map phase and \(T_{Reduce}\) represents the reduce phase time without being affected by the coupled shuffle phase. 
% We use \(T_{overhead}\) to represent the above-mentioned overhead caused by shuffle.
% In the following subsections, we introduce how we decouple the shuffle and use pre-fetching and memory cache to mitigate the overhead.
To mitigate the shuffle overhead, we propose an optimization to overlap the shuffle data transfer in multi-round map tasks, and use memory to cache the shuffle data. To achieve this optimization:
\begin{itemize}
	\item Shuffle phase should be decoupled from reduce phase to achieve a better scheduling scheme.
	\item Reduce tasks should be pre-scheduled in map phase to achieve shuffle data pre-fetching.
\end{itemize}
% In Section \ref{model}, we also propose a performance model called the FRQ to model the optimization.
}

@@

SCache caches the shuffle data on the memory instead of storing on disk liked Spark or Hadoop MapReduce.
In this aspect, SCache optimizes the time of shuffle read and shuffle write since memory gets better I/O performance.
}
% To achieve the decoupling of map tasks and reduce tasks, the original shuffle write and read implementation in the current frameworks should be modified to apply the API of SCache.
% To prevent the release of a slot being blocked by shuffle write,  
% SCache provides a disk-write-like API named $putBlock$ to handle the storage of partitioned shuffle data blocks produced by a map task.
% Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks to SCache's reserved memory and release the slot immediately.
% Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks out of map tasks and store them in the reserved memory.
% After the memory copy, the slot will be released immediately.

@@

To optimize shuffle phase, we propose a co-scheduling scheme with two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}). 
The DAG frameworks follow the co-scheduler to start reduce tasks.
}
% The pre-scheduling and pre-fetching are the most critical aspects of the optimization. 
% The task-node mapping is not determined until tasks are scheduled by the scheduler of DAG framework. 
% Once the tasks are scheduled, the slots will be occupied to launch them. 
% And the shuffle data cannot be pre-fetched without the awareness of task-node mapping.
% We propose a co-scheduling scheme with two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}). 
% That is, the task-node mapping is established a priori, and then it is enforced by the co-scheduler when the DAG framework starts task scheduling.

@@

To illustrate the case, we present a particular spark job which uses the Spark RangePartitioner in Figure \ref{fig:range_pre_sample}. 

@@

Due to the extremely high data skew introduced by the partition, the linear regression model cannot fit the result well.

@@

}
During both predictions, the composition of each reduce partition is calculated as well. We define $prob_i$ as
\begin{equation}
\label{equationprob}
\begin{aligned}
	prob_i &= \max_{0 \leq j \leq m} \frac{BlockSize_{ji}}{reduceSize_i} \\
	m &= \text{number of map tasks}
\end{aligned}
\end{equation}
% Note that a balanced schedule decision can be made under the consideration of the size of each reduce task, and the size of a reduce task produced by one shuffle $reduceSize_i = \sum_{j=0}^{m} {BlockSize_{ji}}$, 
% where the $m$ is the number of map tasks that can be easily extracted from DAG information;
The $reduceSize_i$ represents the size of a reduce task, which is represented by $reduceSize_i = \sum_{j=0}^{m} {BlockSize_{ji}}$.
We use $prob_i$ to achieve a better data locality while performing shuffle pre-scheduling. 
% This parameter is used to achieve a better data locality while performing shuffle pre-scheduling.

\subsubsection{Heuristic MinHeap Scheduling}\label{h-minheap}
% As long as the input sizes of reduce tasks are available, the pre-scheduling is a classic scheduling problem without considering the data locality. 
% But ignoring the data locality can introduce extra network transfer. 
% In order to balance load while minimizing the network traffic, we present the Heuristic MinHeap Scheduling algorithm (Algorithm \ref{hminheap}).
To balance load while minimizing the network traffic, we present the \textit{Heuristic MinHeap Scheduling} algorithm (Algorithm \ref{hminheap}).
{\color{black}
% For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum. 
To keep the pre-scheduling load balance, we maintain a min-heap in the first $while$ loop (i.e., line 6-11).
We use the min-heap to simulate the load of each node and apply the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum.
Spark FIFO only can achieve $2\text{-}approximation$ optimum.
}
% Since the sizes of tasks are considered while scheduling, \textit{Heuristic MinHeap Scheduling} can achieve a shorter makespan than Spark FIFO which is a $2\text{-}approximation$ optimum. 
% Simulation of OpenCloud trace in Figure \ref{fig:sim} also shows that \textit{Heuristic MinHeap Scheduling} has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
After pre-scheduling, the task-node mapping will be adjusted according to the locality. 
The $SWAP\_TASKS$ will be triggered when the $host\_id$ of a task does not equal the $assigned\_id$.
Based on the $prob$, the normalized probability $norm$ is calculated as a bound of performance degradation. 
Inside the $SWAP\_TASKS$, tasks will be selected and swapped without exceeding the $upper\_bound$.
Since the algorithm only maintains a min-heap and traverses $reduce$ for swapping, the algorithm needs $O(n)$ operations.

@@

\begin{minipage}{0.95\columnwidth}
\begin{algorithm}[H]
\caption{Heuristic MinHeap Scheduling for Single Shuffle}
\label{hminheap}
	\begin{algorithmic}[1]
	\small
	\Procedure{schedule}{$m, host\_ids, p\_reduces$}
		\State $m\gets$ partition number of map tasks
		\State $R\gets$ sort $p\_reduces$ by size in non-increasing order
		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
		\State $idx\gets 0$
		\While{$idx <$ len$R$}
		% \Comment{Schedule reduces by MinHeap}
		\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
		\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
		\State $R\left[idx\right].assigned\_id \gets M \left[0\right].host\_id$
		\State Sift down $M\left[0\right]$ by $size$
		\State $idx\gets idx+1$
		\EndWhile
		\State $max\gets$ maximum size in $M$
		% \State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
		\ForAll{$reduce$ in $R$}
		\Comment{Heuristic locality swap}
			\If{$reduce.assigned\_id \neq reduce.host\_id$}
				\State $p\gets reduce.prob$
				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
				\State $upper\_bound \gets \left(1 + norm\right) \times max$
				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
			\EndIf
		\EndFor\newline
		\Return $M$
	\EndProcedure
	\Procedure{swap\_tasks}{$M, reduce, upper\_bound$}
		\State Swap tasks between node $host\_id$ and node $assigned\_id$
		\State of $reduce$ without exceeding the $upper\_bound$
		\State of both nodes.\newline
		% \State Return if it is impossible.
		\Return
	\EndProcedure
	\end{algorithmic}
\end{algorithm}
\end{minipage}

@@

\subsubsection{Cope with Multiple Shuffle Dependencies}
{\color{black}
A reduce stage can have more than one shuffle dependency in the current DAG computing frameworks.
To cope with multiple shuffle dependencies, we present the \textit{Accumulated Heuristic Scheduling} algorithm.
}
% The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
% For those pending shuffles, it is impossible to predict their sizes. 
% This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
% But doing this introduces large overhead such as extra task serialization. 
% To avoid violating the optimization from framework, we present the \textit{Accumulated Heuristic Scheduling} algorithm to cope with multiple shuffle dependencies.
As illustrated in Algorithm \ref{mhminheap}, the sizes of previous \textit{shuffles} scheduled by \textit{Heuristic MinHeap Scheduling} are counted. 
When a new shuffle starts, the predicted $size$, $prob$, and $host\_id$ in $p\_reduces$ are accumulated with previous \textit{shuffles}. 
After scheduling, if the new $assigned\_id$ of a reduce task is not equal the original one, a re-shuffle will be triggered to transfer data to the new host. 
This re-shuffle is rare since the previous shuffle data contributes a huge composition (i.e., high $prob$) after the accumulation, 
which leads to a higher probability of tasks swap in $SWAP\_TASKS$.

### 2019-09-15 scache/tii/tex/relatedwork.tex
Remove blue words
Resubmittion version

{\color{black}
\textbf{Modeling.} 
% Most representative DAG computing frameworks use similar \textit{Bulk Synchronize Parallel} (BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase. 
% , i.e., \textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on. 
% (Hadoop MapReduce can also be considered as a special case of only one superstep in BSP model). 
% In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.
% There are also lots of performance models for MapReduce have been proposed, such as \cite{verma2011aria, khan2016hadoop, herodotou2011hadoop, chen2014cresp, farhat2016stochastic}.
% Verma et al. \cite{verma2011aria} proposed the ARIA model to estimate the required resources based on the job information, the amount of input data and a specified soft deadline.
Khan et al. \cite{khan2016hadoop} proposed the HP model which extends the ARIA model. The HP model adds scaling factors and uses a simple linear regression to estimate the job execution time on larger datasets.
% In \cite{herodotou2011hadoop}, Herodotou proposed a detailed set of mathematical performance models for describing the five phases of a MapReduce job and combine them into an overall MapReduce job model.
% The execution is separated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce. 
% The set of performance models describe each above-mentioned phases and combine into an overall MapReduce job model. 
Chen et al. \cite{chen2014cresp} proposed the CRESP model which is a cost model that estimates the performance of a job then 
% provisions the resources for the job.
Farshid Farhat et al.\cite{farhat2016stochastic} proposed a closed-form queuing model which focuses on stragglers and try to optimize them. 
% The proposed model is parameterized by the task inter-arrival times to the mappers, the delayed tailed service times, and the number of mappers, which is used to optimize the stragglers. 
% \cite{khan2016hadoop, farhat2016stochastic, chen2014cresp} have proposed several methods to model the DAG computing process.
However, the above models are not able to accurately describe the overhead caused by the shuffle process under different scheduling strategies. 
% Different from these models, our FRQ model quantifies computing and I/O resources and visualizes them in the time dimension. 
% The FRQ model focuses on describing the overhead caused by the shuffle process in different scheduling strategies, which satisfies our demand.

\textbf{Industrial big data.}
% In the \textit{Industry 4.0} which leading by the German Government, industrial big data refers to a huge amount of time-series data which generated by industrial equipment in smart factories.
% Industrial big data refers to huge time-series data generated by industrial equipment in smart factories.
More than 1000 Exabytes industrial data is annually generated by smart factories and the data is expected to increase 20-fold in the next ten years \cite{yin2015big}.
Nowadays, the real challenge of big data is not how to collect it, but how to manage it logically and efficiently \cite{lv2017next}.
Several distributed computing frameworks become efficient tools in industrial big data analysis \cite{lade2017manufacturing, li2016scientific}.
% , ur2018big}.
}

{\color{blue}
\textbf{DAG Optimization.} 
% There are a number of studies on DAG optimization.
Slow-start from Hadoop MapReduce is a classic approach to handle shuffle overhead. 
Starfish \cite{starfish} gets sampled data statics for self-tuning system parameters (e.g. slow-start, etc). 
% DynMR \cite{dynmr} dynamically starts reduce tasks in late map stage. 
% All of them have the explicit I/O time in occupied slots. 
% SCache instead starts shuffle pre-fetching without consuming slots. 
iShuffle \cite{guo2017ishuffle} decouples shuffle from reducers and designs a centralized shuffle controller. 
But it can neither handle multiple shuffles nor schedule multiple rounds of reduce tasks. 
iHadoop \cite{ihadoop} aggressively pre-schedules tasks in multiple successive stages to start fetching shuffle. 
% Besides \textit{slow-start} from Hadoop MapReduce, \cite{starfish, ihadoop, guo2017ishuffle, dynmr} have also proposed several methods to improve the DAG frameworks.
% However, we have proved that randomly assigned tasks may hurt the overall performance in Section \ref{randomassign}. 
In data skew mitigation, 
Skewtune \cite{skewtune} partitions the data dynamically. When a straggler task happens, it re-partitions the data and forces them to transfer to other nodes.
% But moving data may cause extra I/O overhead in computing.
LIBRA \cite{chen2014libra} proposes a new sampling method for DAG frameworks and uses an innovative approach, which supports the split of large keys, to balance the load among the reduce tasks.
ToF \cite{zhou2014transformation} proposed a DAG optimization system to address the performance and monetary cost optimizations in the cloud.
Different from these works, SCache pre-schedules multiple shuffles and uses pre-fetching to gain optimization without breaking load balancing. 
%  by combining DAG information and heuristic algorithms.
% \textbf{Delay-scheduling} 
% Delay Scheduling \cite{delay} delays tasks assignment to get better data locality, which can reduce the network traffic. 
% ShuffleWatcher \cite{shufflewatcher} delays shuffle fetching when the network is saturated. 
% At the same time, it achieves better data locality. 
% Both Quincy \cite{quincy} and Fair Scheduling \cite{preemptive} can reduce shuffle data by optimizing data locality of map tasks. 
% But all of them cannot mitigate explicit I/O in both map and reduce tasks. 
% In addition, their optimizations fluctuate under different network performances and data distributions, whereas SCache can provide a stable performance gain by shuffle data pre-fetching and in-memory caching.
}

>>>>

{\color{black}
\textbf{Modeling.} 
% Most representative DAG computing frameworks use similar \textit{Bulk Synchronize Parallel} (BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase. 
% , i.e., \textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on. 
% (Hadoop MapReduce can also be considered as a special case of only one superstep in BSP model). 
% In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.
% There are also lots of performance models for MapReduce have been proposed, such as \cite{verma2011aria, khan2016hadoop, herodotou2011hadoop, chen2014cresp, farhat2016stochastic}.
% Verma et al. \cite{verma2011aria} proposed the ARIA model to estimate the required resources based on the job information, the amount of input data and a specified soft deadline.
Khan et al. \cite{khan2016hadoop} proposed the HP model which extends the ARIA model. The HP model adds scaling factors and uses a simple linear regression to estimate the job execution time on larger datasets.
% In \cite{herodotou2011hadoop}, Herodotou proposed a detailed set of mathematical performance models for describing the five phases of a MapReduce job and combine them into an overall MapReduce job model.
% The execution is separated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce. 
% The set of performance models describe each above-mentioned phases and combine into an overall MapReduce job model. 
Chen et al. \cite{chen2014cresp} proposed the CRESP model which is a cost model that estimates the performance of a job then provisions the resources for the job.
Farshid Farhat et al.\cite{farhat2016stochastic} proposed a closed-form queuing model which focuses on stragglers and tries to optimize them. 
% The proposed model is parameterized by the task inter-arrival times to the mappers, the delayed tailed service times, and the number of mappers, which is used to optimize the stragglers. 
% \cite{khan2016hadoop, farhat2016stochastic, chen2014cresp} have proposed several methods to model the DAG computing process.
However, the above models are not able to accurately describe the overhead caused by the shuffle process under different scheduling strategies. 
% Different from these models, our FRQ model quantifies computing and I/O resources and visualizes them in the time dimension. 
% The FRQ model focuses on describing the overhead caused by the shuffle process in different scheduling strategies, which satisfies our demand.

\textbf{Industrial big data.}
% In the \textit{Industry 4.0} which leading by the German Government, industrial big data refers to a huge amount of time-series data which generated by industrial equipment in smart factories.
% Industrial big data refers to huge time-series data generated by industrial equipment in smart factories.
More than 1000 Exabytes industrial data is annually generated by smart factories and the data is expected to increase 20-fold in the next ten years \cite{yin2015big}.
Nowadays, the real challenge of big data is not how to collect it, but how to manage it logically and efficiently \cite{lv2017next}.
Several distributed computing frameworks become efficient tools in industrial big data analysis \cite{lade2017manufacturing, li2016scientific, ur2018big}.
}

{\color{black}
\textbf{DAG Optimization.} 
% There are a number of studies on DAG optimization.
Slow-start from Hadoop MapReduce is a classic approach to handle shuffle overhead. 
Starfish \cite{starfish} gets sampled data statics for self-tuning system parameters (e.g. slow-start, etc). 
% DynMR \cite{dynmr} dynamically starts reduce tasks in late map stage. 
% All of them have the explicit I/O time in occupied slots. 
% SCache instead starts shuffle pre-fetching without consuming slots. 
iShuffle \cite{guo2017ishuffle} decouples shuffle from reducers and designs a centralized shuffle controller. 
But it can neither handle multiple shuffles nor schedule multiple rounds of reduce tasks. 
iHadoop \cite{ihadoop} aggressively pre-schedules tasks in multiple successive stages to start fetching shuffle. 
% Besides \textit{slow-start} from Hadoop MapReduce, \cite{starfish, ihadoop, guo2017ishuffle, dynmr} have also proposed several methods to improve the DAG frameworks.
% However, we have proved that randomly assigned tasks may hurt the overall performance in Section \ref{randomassign}. 
In data skew mitigation, 
Skewtune \cite{skewtune} partitions the data dynamically. When a straggler task happens, it re-partitions the data and forces them to transfer to other nodes.
% But moving data may cause extra I/O overhead in computing.
LIBRA \cite{chen2014libra} proposes a new sampling method for DAG frameworks and uses an innovative approach, which supports the split of large keys, to balance the load among the reduce tasks.
ToF \cite{zhou2014transformation} proposed a DAG optimization system to address the performance and monetary cost optimizations in the cloud.
Different from these works, SCache pre-schedules multiple shuffles and uses pre-fetching to gain optimization without breaking load balancing. 
%  by combining DAG information and heuristic algorithms.
% \textbf{Delay-scheduling} 
% Delay Scheduling \cite{delay} delays tasks assignment to get better data locality, which can reduce the network traffic. 
% ShuffleWatcher \cite{shufflewatcher} delays shuffle fetching when the network is saturated. 
% At the same time, it achieves better data locality. 
% Both Quincy \cite{quincy} and Fair Scheduling \cite{preemptive} can reduce shuffle data by optimizing data locality of map tasks. 
% But all of them cannot mitigate explicit I/O in both map and reduce tasks. 
% In addition, their optimizations fluctuate under different network performances and data distributions, whereas SCache can provide a stable performance gain by shuffle data pre-fetching and in-memory caching.
}
